{\it Proposal:}\\ Ultrashort pulsed microwave viral envelope disruption as a COVID-19 treatment

### 2020-10-19 documents/pseudo_soliton.tex
DNA
Reconstruction just fine

>>>>

There are some extremely tricky subtleties in the simulation.  \cite{propagation1992}. In \cite{Comments1993}, Leubbers says FDTD and FFT both are better than Asympt, Ogh says no there's no problem, Asymptotic is really accurate. Frankly, I can't make heads or tails of any of these, not understanding the asymptotic method at all.
